### 2015-03-02 ThesisJo/introduction.tex
la2pdf commit - 2015:03:02	16:50:06	(Mon 2.Mar)

When a rock is thrown into a pound of water it abruptly displaces water at the location of impact. This is an unstable state where various physical forces compete for order. Gravity wants the water back where it wants, but due to inertia the mass will resist any change in its motion. The wrestling of these forces result in a spherical wave propagating from the displacement centre.

>>>>

When a rock is thrown into a pound of water it abruptly displaces water at the location of impact.
%This is an unstable state where various physical phenomena wrestle for control. Gravity wants the water back where it was, inertia cause the mass to resist any change in its state of motion.
This results in spherical waves propagating from the displacement center. On the surface is a wave that has particles moving in circles relative to the propagation direction, while in the depths particles will move parallel to the propagation direction, alternately being compressed and spread apart. Sound is pressure waves.

Unlike electromagnetic waves, these
